Matching Bullets

### 2015-11-24 imaging-paper.Rnw
Fitted and residual images for Loess fit

Next, we fit a Loess regression to the data.

\hh{XXX could you include a series of plots here, walking through the individual steps of this list? I like the ones that you've already got in the loess fit function ... }

>>>>

Next, we fit a Loess regression to the data. Figure \ref{fig:loess_fit} provides a look at the Loess fit, in blue, overlayed against the processed image of part 1 of bullet 1. The fit seems to do a reaosnable job of capturing the structure of the image. Figure \ref{fig:loess_resid} shows the residuals from this fit. It is clear that there is a rather significant amount of autocorrelation, which make sense given the presence of striations and markings. Certainly, tuning the parameters for this regression, such as the Loess span, could prove to do an even better job at making the markings more clear.
